---
output:
  md_document:
    variant: markdown_github
---

[![Linux Build Status](https://travis-ci.org/AustralianAntarcticDivision/bgmfiles.svg?branch=master)](https://travis-ci.org/AustralianAntarcticDivision/bgmfiles)
[![Windows Build Status](https://ci.appveyor.com/api/projects/status/github/AustralianAntarcticDivision/bgmfiles?branch=master&svg=true)](https://ci.appveyor.com/project/AustralianAntarcticDivision/bgmfiles)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/bgmfiles)](https://cran.r-project.org/package=bgmfiles)
[![Coverage Status](https://img.shields.io/codecov/c/github/AustralianAntarcticDivision/bgmfiles/master.svg)](https://codecov.io/github/AustralianAntarcticDivision/bgmfiles?branch=master)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# BGM files for Atlantis

A raw-data package with example .bgm files (box geometry model) for Atlantis. 

**PLEASE NOTE:** this is not an official source of BGM for use in Atlantis. 

See https://github.com/mdsumner/rbgm for an R package to read these files and work with the box geometry. 

## Installation

Install from Github using `devtools`. 

```{r,eval=FALSE}
# install.packages("devtools")
devtools::install_github("AustralianAntarcticDivision/bgmfiles")
```

## Usage 

List the available raw files available in this package. 

```{r}
library(bgmfiles)
files <- bgmfiles()
print(basename(files))
```

If we need to we can also filter based on a specific string with the `pattern` argument: 

```{r}
afiles <- bgmfiles(pattern = "^antarc")
print(basename(afiles))

```
This package is really just a data package to install the example files, the function `bgmfiles` is ridiculously simple this is all it does: 

```{r}
files <- list.files(system.file("extdata", package = "bgmfiles"), recursive = TRUE, full.names = TRUE)

print(basename(files))

```

We don't really need to load or attach the package to find these files, but using the installation mechanism is very convenient for R use.  


## Contribute!

If you would like to contribute example BGM files, please see https://github.com/AustralianAntarcticDivision/box-geometry-models or just get in touch directly. 



